Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-08 ms/main.tex
small change
Fix figure 5

%%% Figure: Spatial model - global selection
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.56]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_a}.pdf} \\
    ~
    \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

%%% Figure: invasion
\begin{figure}[b]
  \centering
   \includegraphics[scale=0.4]{Frequency_of_invadors.eps}
    ~
    \includegraphics[scale=0.4]{Frequency_of_cooperation_after_invasion.eps}\\ 
  \caption{
  \textbf{Evolution of social association.} successful invasion of new modifier allele m; starting from stable coexistence of cooperators and defactors with soical association $\alpha_1$. 
  The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
  \textbf{(a)} describes the frequency of the invadors. 
  \textbf{(b)} describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency $\hat{p}_2^*$ which described by the black dashed line. 
  $\hat{p}_2^*$ is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.
  In this case $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.
  }
  \label{fig:invasion}
\end{figure}

>>>>

%%% Figure: Spatial model - global selection
\begin{figure}[p]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.45]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection_withSmallBox_B}.pdf} \\
    ~
    \includegraphics[scale=0.65]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
  \caption{
  \textbf{Evolution of cooperation in a structured population.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries_v_threshold}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

%%% Figure: invasion
\begin{figure}[b]
  \centering
   \includegraphics[scale=0.5]{Frequency_of_invadors.eps}
  \caption{
  \textbf{Evolution of social association.} successful invasion of new modifier allele m; starting from stable coexistence of cooperators and defactors with soical association $\alpha_1$. 
  The invadors have modifier allele m which cause different soical association value, $\alpha_2$ where $\alpha_2<\alpha_1$.
  The blue curve describes the frequency of the invadors, starting from initial frequency of 1\%.
  The orange curve describes the frequency of cooperators after invasion. The frequency of cooperators decreases towards new stable frequency which is described by the black dashed line. 
  The frequency of cooperators after the fixation of the invadors is the equilibrium described in \autoref{eq:general_equilibrium} with soical association $\alpha=\alpha_2$.
  In this case $T_A = 0.4$, $T_B = 0.7$, $b=1.3$, $c=0.05$, $\alpha_1 = 0.7$ and $\alpha_2 = 0.65$.
  }
  \label{fig:invasion}
\end{figure}
